---
title: "SBECON scRNA-Seq"
author: "Maria A. Sierra"
date: "1/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(installr)
library(dplyr)
library(Seurat)
library(ggplot2)
library(msigdbr)
library(fgsea)
library(dplyr)
library(tibble)
library(escape)
library(dittoSeq)
library(EnrichmentBrowser)
```

## scRNA-seq pipeline mice dataset
This is the processing pipeline used to analyse and generate figures from ovarian cancer mouse dataset

### Import data
```{r import_data}
scbecon.data<-Read10X(data.dir = "path/to/folder/10Xdata")
```

### Subset low quality data
```{r quality_data}
scbecon<-CreateSeuratObject(scbecon.data, project="scbecon", min.cells=3, min.features=200)
scbecon@meta.data %>% head()
length(colnames(scbecon)) # No. of cells
scbecon[["percent.mt"]]<-PercentageFeatureSet(object=scbecon, pattern = "^mt-")
scbecon_subset <- subset(x = scbecon, subset = nFeature_RNA > 200 & nFeature_RNA < 
                           2500 & percent.mt < 5)
length(colnames(scbecon_subset)) # No. of cells after subsetting low quality data
```

### Normalize data
```{r norm}
scbecon_subset_log <- NormalizeData(object = scbecon_subset, 
                                    normalization.method = "LogNormalize", 
                                    scale.factor = 10000)
```
### Identification of highly variable features (feature selection)
```{r variable_features}
scbecon_variable <- FindVariableFeatures(scbecon_subset_log, selection.method = "vst", nfeatures = 2000)
#top10<-head(x=VariableFeatures(scbecon_variable),10)
```

### Scaling the data
```{r scaling}
all.genes<-rownames(scbecon_variable)
scbecon_scaled<-ScaleData(scbecon_variable, features = all.genes)
```

### Perform linear dimensional reduction
```{r linear_dim_reduc}
scbecon_pca <- RunPCA(scbecon_scaled, features = VariableFeatures(object = scbecon_scaled))
```

### Cluster cells
```{r clustering}
scbecon_cluster<-FindNeighbors(scbecon_pca,dims = 1:20, nn.method = "rann")
scbecon_cluster<-FindClusters(scbecon_cluster, resolution =0.25)
head(x=Idents(scbecon_cluster),10)
```

### Non-linear dimensional reduction (UMAP/tSNE)
```{r non_linear_dim_reduc}
scbecon_umap<-RunUMAP(scbecon_cluster,dims = 1:10)
DimPlot(scbecon_umap,reduction = "umap", label = T) +
  theme_classic() +
  theme(axis.text = element_text(size=15, color="black"), legend.position = "none",
        axis.title = element_text(size=15, color="black")) 
```

### ssGSEA in all cluster groups <GO:BP>

Enrichment on the RNA count data. This is computationally intensive and is highly dependent on the number of cells and the number of gene sets included.

```{r ssgsea_by_allgroup_gobp}
library(org.Mm.eg.db)
mmu_gene_set_c5=getGenesets(org="mmu",db ="msigdb",gene.id.type = "SYMBOL",cache = TRUE,
  return.type = c("GeneSetCollection"),cat = "C5" ) #subcat="GO:BP"

gene_set_iron=mmu_gene_set_c5[grep("IRON_",names(mmu_gene_set_c5))]
gene_set_iron=gene_set_iron[-grep("M26433",names(gene_set_iron))]
gene_set_iron=gene_set_iron[-grep("_HP_",names(gene_set_iron))]

ES.seurat <- enrichIt(obj = scbecon_umap, gene.sets = gene_set_iron)
```

### Merge with seurat object

Add enrichment results to the Seurat object
```{r add_to_Seurat}
scbecon_umap_ES <- Seurat::AddMetaData(scbecon_umap, ES.seurat)
```

### Heatmap all cluster groups
```{r heatmap_ssgsea_allclusters}
my_levels <- c(0,3,6,9,1, 2, 4, 5,7,8,10)
scbecon_umap_ES@meta.data$seurat_clusters <- factor(x = scbecon_umap_ES@meta.data$seurat_clusters, levels = my_levels)
ggplotColours <- function(n = 6, h = c(0, 360) + 15){
   if ((diff(h) %% 360) < 1) h[2] <- h[2] - 360/n
   hcl(h = (seq(h[1], h[2], length = n)), c = 100, l = 65)
 }
ggplotColours(n = 11)

dittoHeatmap(scbecon_umap_ES, genes = NULL, metas = names(ES.seurat), 
             annot.by = "seurat_clusters", heatmap.colors = colorRampPalette(c("blue", "white", "red"))(50),
             fontsize = 7,annot.colors = c("#F8766D" ,"#64B200","#00BADE","#EF67EB" ,"#DB8E00" ,"#AEA200" ,"#00BD5C" ,"#00C1A7" ,"#00A6FF","#B385FF" ,"#FF63B6"),
             cluster_cols = F, breaks= brks)
```






